---
title: "Project Report"
author: "Pletiuk R M"
date: "2023-11-12"

output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project "CodeCurrencies: Decoding IT Salaries through R Analysis" 

In this project, I aim to analyze the salaries of IT professionals using R software. I will compile and analyze a dataset, visualizing various aspects of salaries through diverse graphs. Additionally, I will calculate descriptive statistics, construct at least 7 simple linear regression models, and build 5 multiple linear regression models to explore relationships between economic variables and IT salaries. Finally, I will create a report in R, presenting the findings and drawing conclusions on the factors influencing IT salaries. 

## Plan:

- Descriptive statistics
- Plots
- Pair regression
- Multiple regression

## Descriptive statistics (part 1)

Descriptive statistics of variables:

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5, out.width='70%', fig.align='center'}
library(readxl)
my_data1 <- read_excel("data.xlsx", col_types = c("skip", 
    "skip", "skip", "skip", "skip", "numeric", 
    "skip", "numeric", "skip", "skip", "numeric", 
    "skip", "skip", "skip"))
library(dplyr)

summary(my_data1)
```

## Descriptive statistics (part 2)

Descriptive statistics of variables:

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5, out.width='70%', fig.align='center'}
library(readxl)
my_data1 <- read_excel("data.xlsx", col_types = c("skip", 
    "skip", "skip", "skip", "numeric", "skip", 
    "skip", "skip", "skip", "skip", "skip", 
    "numeric", "skip", "numeric"))
library(dplyr)

summary(my_data1)
```

## Plot "Average Number of Projects vs Type of Employment"

```{r,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5}

library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))

library(ggplot2)

# Ваш код діаграми
ggplot(my_data, aes(x = Type_of_employment, y = Number_of_projects, fill = Type_of_employment)) +
  geom_bar(stat = "summary", fun = "mean", position = "dodge") +
  labs(title = "Average Number of Projects vs Type of Employment",
       x = "Type of Employment",
       y = "Average Number of Projects",
       fill = "Type of Employment") +
  theme_minimal()

```


## Plot "Percentage Distribution of Continent"

```{r,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5}

library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))

library(ggplot2)

# Ваш код діаграми
ggplot(my_data, aes(x = "", fill = Continent)) +
  geom_bar(width = 1, color = "white", position = "fill") +
  geom_text(stat = "count", aes(label = scales::percent(..count../sum(..count..))), position = position_fill(vjust = 0.5)) +
  labs(title = "Percentage Distribution of Continent") +
  theme_minimal()

```

## Plot "Scatter Plot of Salary vs Age"

```{r,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5}

library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))

library(ggplot2)

ggplot(my_data, aes(x = Age, y = Salary, color = Specialization)) +
  geom_point() +
  labs(title = "Scatter Plot of Salary vs Age",
       x = "Age",
       y = "Salary",
       color = "Specialization") +
  theme_minimal()

```

## Plot "Boxplot of Salary by Specialization"

```{r,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5}

library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))

library(ggplot2)

ggplot(my_data, aes(x = Specialization, y = Salary, fill = Specialization)) +
  geom_boxplot() +
  labs(title = "Boxplot of Salary by Specialization",
       x = "Specialization",
       y = "Salary",
       fill = "Specialization") +
  theme_minimal()

```

## Plot "Line Plot of Age vs Experience"

```{r,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5}

library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))

library(ggplot2)

ggplot(my_data, aes(x = Experience, y = Age, group = 1)) +
  geom_line(color = "green") +
  geom_point(color = "green", size = 2) +
  labs(title = "Line Plot of Age vs Experience",
       x = "Experience",
       y = "Age") +
  theme_minimal()

```

## Plot "Salary by Specialization and Education"

```{r,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5}

library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))

library(ggplot2)

ggplot(my_data, aes(x = Specialization, y = Salary, fill = Education)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Grouped Bar Chart of Salary by Specialization and Education",
       x = "Specialization",
       y = "Salary",
       fill = "Education") +
  theme_minimal()

```

## These are the pairwise regressions

1. Salary ~ Experience
2. Salary ~ Hour on week
3. Salary ~ Age
4. Salary ~ Number of projects
5. Salary ~ Job satisfaction
6. Salary ~ Additional profit
7. Number of projects ~ Experience

##  Linear pair Regression: Experience vs Salary (1)

- Plot Linear pair Regression

```{r,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5}
library(readxl)
my_data3 <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))


library(ggplot2)

# Побудова графіка та лінійної регресії для "Experience" та "Salary"
regression_plot1 <- ggplot(my_data3, aes(x = Experience, y = Salary)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  labs(title = "Linear Regression: Experience vs Salary",
       x = "Experience",
       y = "Salary")

print(regression_plot1)

```

## Linear pair Regression: Experience vs Salary (2)

```{r,  echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=8, fig.height=5}
library(readxl)
my_data3 <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))


model11 <- lm(Salary ~ Experience, data = my_data3)

summary(model11)

 library(broom)

 tidy_model <- tidy(model11)
 
# Вивід рівняння регресії 
cat("Regression Equation: Salary =", tidy_model$estimate[1],"\n", " + ", tidy_model$estimate[2], " * Experience\n")

```


## Linear pair Regression: Number of projects vs Experience (1)

- Plot Linear pair Regression

```{r,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5}
library(readxl)
my_data3 <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))


library(ggplot2)

# Побудова графіка та лінійної регресії для "Experience" та "Salary"
regression_plot7 <- ggplot(my_data3, aes(x = Experience, y = Number_of_projects)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "green") +
  labs(title = "Linear Regression: Experience vs Number_of_projects",
       x = "Experience",
       y = "Number_of_projects")

print(regression_plot7)

```

## Linear pair Regression: Number of projects vs Experience (2)

```{r,  echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=8, fig.height=5}
library(readxl)
my_data3 <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))

madel71 <- lm(Number_of_projects ~ Experience, data = my_data3)


summary(madel71)

 library(broom)

 tidy_model <- tidy(madel71)
 
# Вивід рівняння регресії 
cat("Regression Equation: Number_of_projects =", tidy_model$estimate[1],"\n", " + ", tidy_model$estimate[2], " * Experience\n")

```


## Other pairwise regressions

```{r,  echo=FALSE, message=FALSE, warning=FALSE ,   fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))

model21 <- lm(Salary ~ Hour_on_week, data = my_data)
model31 <- lm(Salary ~ Age, data = my_data)
model41 <- lm(Salary ~ Number_of_projects, data = my_data)
model51 <- lm(Salary ~ Job_satisfaction, data = my_data)
model61 <- lm(Salary ~ Additional_profit, data = my_data)

 library(broom)

tidy_model2 <- tidy(model21) 
tidy_model3 <- tidy(model31) 
tidy_model4 <- tidy(model41) 
tidy_model5 <- tidy(model51) 
tidy_model6 <- tidy(model61) 

# Вивід рівняння регресії 
cat("Regression Equation: \n")
cat(">Salary vs Hour on week: Salary =", tidy_model2$estimate[1], " + \n", tidy_model2$estimate[2], " * Hour_on_week\n")
cat(">Salary vs Age: Salary =", tidy_model3$estimate[1], " + ", tidy_model3$estimate[2], " * Age\n")
cat(">Salary vs Number of projects: Salary =", tidy_model4$estimate[1], " + \n", tidy_model4$estimate[2], " * Number_of_projects\n")
cat(">Salary vs Job satisfaction: Salary =", tidy_model5$estimate[1], " + \n", tidy_model5$estimate[2], " * Job_satisfaction\n")
cat(">Salary vs AgAdditional profite: Salary =", tidy_model6$estimate[1], " + \n", tidy_model6$estimate[2], " * Additional_profit\n")


```

## Other pairwise regressions (1) 

-  Salary ~ Hour_on_week:
 
```{r,  echo=FALSE, message=FALSE, warning=FALSE,  fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))

model21 <- lm(Salary ~ Hour_on_week, data = my_data)

summary(model21)$coefficients[, c("Estimate", "Std. Error", "t value", "Pr(>|t|)")]
 
```

```{r,  echo=FALSE, message=FALSE, warning=FALSE, results='asis',  fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))

model21 <- lm(Salary ~ Hour_on_week, data = my_data)

 library(broom)
tidy_model2 <- tidy(model21) 
# Вивід рівняння регресії 
cat("Regression Equation:\n")
cat("Salary vs Hour on week: Salary =", tidy_model2$estimate[1], " + ", tidy_model2$estimate[2], " * Hour_on_week\n")

```

- Salary ~ Age:

```{r,  echo=FALSE, message=FALSE, warning=FALSE,  fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))


model31 <- lm(Salary ~ Age, data = my_data)
summary(model31)$coefficients[, c("Estimate", "Std. Error", "t value", "Pr(>|t|)")]

 
```

```{r,  echo=FALSE, message=FALSE, warning=FALSE, results='asis',  fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))


model31 <- lm(Salary ~ Age, data = my_data)

 library(broom)

tidy_model3 <- tidy(model31) 
# Вивід рівняння регресії 
cat("Regression Equation:\n")
cat("Salary vs Age: Salary =", tidy_model3$estimate[1], " + ", tidy_model3$estimate[2], " * Age\n")

```

## Other pairwise regressions (2) 

- Salary ~ Number of projects

```{r,  echo=FALSE, message=FALSE, warning=FALSE ,   fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))


model41 <- lm(Salary ~ Number_of_projects, data = my_data)
summary(model41)$coefficients[, c("Estimate", "Std. Error", "t value", "Pr(>|t|)")]

```

```{r,  echo=FALSE, message=FALSE, warning=FALSE , results='asis',  fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))


model41 <- lm(Salary ~ Number_of_projects, data = my_data)

 library(broom)

tidy_model4 <- tidy(model41) 

# Вивід рівняння регресії 
cat("Regression Equation: \n")
cat(">Salary vs Number of projects: Salary =", tidy_model4$estimate[1], " + \n", tidy_model4$estimate[2], " * Number_of_projects\n")

```

- Salary ~ Job satisfaction

```{r,  echo=FALSE, message=FALSE, warning=FALSE ,   fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))


model51 <- lm(Salary ~ Job_satisfaction, data = my_data)
summary(model51)$coefficients[, c("Estimate", "Std. Error", "t value", "Pr(>|t|)")]
 
```

```{r,  echo=FALSE, message=FALSE, warning=FALSE ,   fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))


model51 <- lm(Salary ~ Job_satisfaction, data = my_data)

 library(broom)

tidy_model5 <- tidy(model51) 
 
# Вивід рівняння регресії 
cat("Regression Equation: \n")
cat(">Salary vs Job satisfaction: Salary =", tidy_model5$estimate[1], " + \n", tidy_model5$estimate[2], " * Job_satisfaction\n")

```


## Other pairwise regressions (3) 

- Salary ~ Additional profit

```{r,  echo=FALSE, message=FALSE, warning=FALSE ,   fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))


model61 <- lm(Salary ~ Additional_profit, data = my_data)
summary(model61)$coefficients[, c("Estimate", "Std. Error", "t value", "Pr(>|t|)")]

```

```{r,  echo=FALSE, message=FALSE, warning=FALSE , results='asis',  fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))


model61 <- lm(Salary ~ Additional_profit, data = my_data)

 library(broom)

tidy_model6 <- tidy(model61) 

# Вивід рівняння регресії 
cat("Regression Equation: \n")
cat(">Salary vs Additional profit: Salary =", tidy_model6$estimate[1], " + \n", tidy_model6$estimate[2], " * Additional_profit\n")

```





## Multiple regressions

-  Salary ~ Experience + Hour_on_week
-  Salary ~ Experience + Number_of_projects
-  Salary ~ Experience + Additional_profit
-  Salary ~ Experience + Job_satisfaction
-  Salary ~ Hour_on_week + Number_of_projects + Additional_profit + Job_satisfaction



## Multiple Regression: Experience + Number_of_projects vs Salary (1)

- Plot Multiple  Regression

```{r,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))


library(ggplot2)

# Побудова графіка та лінійної регресії для "Experience" та "Salary"
regression_plot1 <- ggplot(my_data, aes(x = Experience, y = Salary)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  labs(title = "Linear Regression: Experience vs Salary",
       x = "Experience",
       y = "Salary")

# Побудова графіка та лінійної регресії для "Number_of_projects" та "Salary"
regression_plot2 <- ggplot(my_data, aes(x = Number_of_projects, y = Salary)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  labs(title = "Linear Regression: Number_of_projects vs Salary",
       x = "Number_of_projects",
       y = "Salary")


library(gridExtra)
grid.arrange(regression_plot1, regression_plot2, ncol = 2)

```


## Multiple Regression: (2)

```{r,  echo=FALSE, message=FALSE, results='asis', warning=FALSE, fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))

madel22 <- lm(Salary ~ Experience + Number_of_projects, data = my_data)

summary(madel22)

 library(broom)

 tidy_model <- tidy(madel22)
 
# Вивід рівняння регресії 
cat("Regression Equation: Salary =", tidy_model$estimate[1],"\n", 
    " + ", tidy_model$estimate[2], " * Experience\n",
    " + ", tidy_model$estimate[3], " * Number_of_projects\n")

```





## Other Multiple Regressions (1)

-  Salary ~ Experience + Hour_on_week:

```{r,  echo=FALSE, message=FALSE, warning=FALSE , results='asis',   fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))

# Побудова множинної лінійної регресійної моделі
model12 <- lm(Salary ~ Experience + Hour_on_week, data = my_data)

 library(broom)

tidy_model2 <- tidy(model12) 

# Вивід рівняння регресії 
cat("Regression Equation: Salary =", tidy_model2$estimate[1],"\n", 
    " + ", tidy_model$estimate[2], " * Experience\n",
    " + ", tidy_model$estimate[3], " * Hour_on_week\n")

```

-  Salary ~ Experience + Additional_profit

```{r,  echo=FALSE, message=FALSE, warning=FALSE , results='asis',   fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))

# Побудова множинної лінійної регресійної моделі
model32 <- lm(Salary ~ Experience + Additional_profit, data = my_data)

 library(broom)

tidy_model3 <- tidy(model32) 

# Вивід рівняння регресії 
cat("Regression Equation: Salary =", tidy_model3$estimate[1],"\n", 
    " + ", tidy_model$estimate[2], " * Experience\n",
    " + ", tidy_model$estimate[3], " * Additional_profit\n")
```


## Other Multiple Regressions (2)

-  Salary ~ Experience + Job_satisfaction

```{r,  echo=FALSE, message=FALSE, warning=FALSE , results='asis',   fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))

# Побудова множинної лінійної регресійної моделі
model42 <- lm(Salary ~ Experience + Job_satisfaction, data = my_data)

 library(broom)

tidy_model4 <- tidy(model42) 

# Вивід рівняння регресії 
cat("Regression Equation: Salary =", tidy_model3$estimate[1],"\n", 
    " + ", tidy_model$estimate[2], " * Experience\n",
    " + ", tidy_model$estimate[3], " * Job_satisfaction\n")
```




## Other Multiple Regressions (3)

-  Salary ~ Hour_on_week + Number_of_projects + Additional_profit + Job_satisfaction

```{r,  echo=FALSE, message=FALSE, warning=FALSE ,    fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))

# Побудова множинної лінійної регресійної моделі
model52 <- lm(Salary ~ Hour_on_week + Number_of_projects + Additional_profit + Job_satisfaction, data = my_data)
summary(model52)$coefficients[, c("Estimate", "Std. Error", "t value", "Pr(>|t|)")]
      
```

```{r,  echo=FALSE, message=FALSE, warning=FALSE , results='asis',   fig.width=8, fig.height=5}
library(readxl)
my_data <- read_excel("data.xlsx", col_types = c("numeric", 
    "text", "text", "text", "numeric", "numeric", 
    "text", "numeric", "text", "text", "numeric", 
    "numeric", "numeric", "numeric"))

# Побудова множинної лінійної регресійної моделі
model52 <- lm(Salary ~ Hour_on_week + Number_of_projects + Additional_profit + Job_satisfaction, data = my_data)


 library(broom)
tidy_model5 <- tidy(model52) 
 
# Вивід рівняння регресії 
cat("Regression Equation: Salary =", tidy_model5$estimate[1],"\n", 
    " + ", tidy_model5$estimate[2], " * Hour_on_week\n",
    " + ", tidy_model5$estimate[3], " * Number_of_projects\n",
    " + ", tidy_model5$estimate[4], " * Additional_profit\n",
    " + ", tidy_model5$estimate[5], " * Job_satisfaction\n")
      
```





## Conclusion

### Insights and Trends

The analysis revealed key insights into IT salaries, showcasing trends through descriptive statistics and diverse visualizations.

### Regression Models

Constructed simple and multiple linear regression models provided a deeper understanding of the impact of economic variables on IT salaries, offering valuable predictive capabilities.

### Future Considerations

These findings have implications for strategic HR decisions, and future research could explore industry-specific nuances for a more nuanced perspective.